---
title: "Grade Report of the Random Students in 2020 Semestre"
author: "Atilla Özgür"
date: "10/7/2020"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Grades Summary

```{r read_grades, message = FALSE, echo=FALSE}
library(readr)
df_grades <- read_csv("../data/grades.csv", locale = locale(encoding = "ISO-8859-1"))

```
Note that `message=False` parameter used to suppress warnings from read_csv about column specification


```{r grades}
summary(df_grades)
```

## Grades Histogram

You can also embed plots, for example:

```{r pressure,warning=FALSE, echo=FALSE}
library(ggplot2)
# Basic histogram
p = ggplot(df_grades, aes(x=grades))  + 
        geom_histogram(binwidth=5)
print(p)
```


Note that `warning=False` parameter used to suppress warnings from ggplot

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Lab TODO

1. if cut off for failing is 60, show how many students are failing.

```{r failing_student_count,warning=FALSE, echo=FALSE}
failing_student_count = sum(df_grades$grades < 60)

```
we have total of `r failing_student_count` students failing the class with a grade of lower than 60.

2. if A+ grades is given to 97 or higher, show how many students got this grade.

```{r Aplus_student_count,warning=FALSE, echo=FALSE}
Aplus_student_count = sum(df_grades$grades >= 97)

```
we have total of `r Aplus_student_count` students with A+ grade with a numerical grade of 97 or higher.


